Data Management for LSST Special Programs

### 2023-05-20 sec_proc.tex
Update sec_proc.tex

As described in Section~\ref{ssec:proc_wfd}, in some cases the science goals 
of a Special Program might be met by including the data in the WFD data 
products; especially the Prompt or DIA data products for standard visits.
Thus, most of the RDM-generated data products considered below are for 
static-sky Data Release data products, or data products for non-standard visits.

@@

Decisions about when to produce separate Special Programs data products are 
left to the discretion of RDM.
Appendix~\ref{sec:spcs} provides more detailed, step-by-step data processing 
examples for some potential Special Programs as further illustration.

@@

\subsubsection{Target-of-Opportunity (TOO)}

Options for RDM to process TOO, especially during the first year of Operations 
when the template coverage will be low, are discussed in more detail in 
\citeds{rtn-008}.

@@

For science goals that require data products which are not possible to create with 
the original or reconfigured versions of the 
LSST Science Pipelines, and/or for which new algorithmic development or significant 
computational resources are needed, 
user-designed and user-run processing will be needed.

As described above, custom coadds (e.g., weekly, monthly) are also left to users 
to generate, as required by their specific science goals.

@@

Short-exposure images obtained during twilight, which will have a very bright sky 
background unlike other LSST images, might require User-Generated algorithms to 
subtract the high sky background.

@@

Mini-surveys with time-domain science goals that aren't met by the Prompt pipelines, 
e.g., those that require difference imaging with coadded images on an intermediate 
timescale (e.g., a weekly stack), might require user-generated processing.

>>>>

As described in Section~\ref{ssec:proc_wfd}, in some cases the science goals 
of a Special Program might be met by including the data in the WFD data 
products; especially the Prompt or DIA data products for standard visits.
Thus, most of the RDM-generated data products considered below are for 
static-sky Data Release data products, or data products for non-standard visits.
Decisions about when to produce separate Special Programs data products are 
left to the discretion of RDM.

@@

@@

\subsubsection{Target-of-Opportunity (TOO) Observations}

Options for RDM to process TOO observations, especially during the first year of Operations 
when the template coverage will be low, are discussed in more detail in 
\citeds{rtn-008}.

@@

Science goals that require data products which are not possible to create with 
the original or reconfigured versions of the LSST Science Pipelines, 
and/or for which new algorithmic development or significant computational resources 
are needed, will require user processing and user-generated data products.
As described above, custom coadds (e.g., weekly, monthly) are also left to users 
to generate, as required by their specific science goals.

@@

Short-exposure images obtained during twilight, which will have a very bright sky 
background unlike other LSST images, might require user-generated algorithms to 
subtract the high sky background.

@@

Mini-surveys with time-domain science goals that aren't met by the Prompt pipelines, 
e.g., those that require difference imaging with coadded images on an intermediate 
timescale (e.g., a weekly stack), would require user-generated processing.
